A continuous urbanization index to assess phylogenetic adaptations in urban bird living

### 2018-05-07 ms.Rmd
working on manuscript creation workflow

# RESULTS
A total of 637,482 checklists provided a total of 5,944,819 observations of 580 different species which had > 100 observations. The least recorded species was Black-breasted Buttonquail (N=104) while the most recorded species was Australian Magpie (N=158,615). The mean ï¿½ SD number of observations for a species was 10,250 ï¿½ 19,269.19. Density plots of all 580 species' distributions of average radiance values are presented in Appendix 3.

@@

```{r Figure 1, echo=FALSE, fig.cap="An example of five different species' average radiance values."}
knitr::include_graphics("final figures for paper/Figure1.pdf")
```

```{r Figure 2, echo=FALSE, fig.cap="The distribution, on a log-scale, of the response variable for the 477 species included in the analysis, with five example species highlighted."}
knitr::include_graphics("final figures for paper/Figure2.pdf")
```

```{r Figure 3, echo=FALSE, fig.cap="A phylogenetic tree of the birds with the tips colored based on the urbanization index. The urbanization index is also shown based on the size of the bar associated with a species."}
knitr::include_graphics("final figures for paper/Figure3.pdf")
```

```{r Figure 4, echo=FALSE, fig.cap="Parameter estimates for each of the four modelling approaches employed in the analysis. A star represents a significant effect. Note that the model-averaged results do not contain every possible predictor variable in the case that a given predictor variable was not included in the top model set."}
knitr::include_graphics("final figures for paper/Figure4.pdf")
```

```{r Figure 5, echo=FALSE, fig.cap="Proportional differences for parameter estimates from the non-phylogenetically constrained and phylogenetically constrained models."}
knitr::include_graphics("final figures for paper/Figure5.pdf")
```

@@

```{r Figure S1, echo=FALSE, fig.cap="A correlation plot for the continuous variables used in the modelling procedures."}
knitr::include_graphics("figures/corrplot_of_continuous_variables.pdf")
```

```{r Figure S2, echo=FALSE, fig.cap="Phylogenetic uncertainty for some of the most important predictor variables included in the analysis."}
knitr::include_graphics("figures/accounting_for_phylo_uncertainty.pdf")
```

# Supplementary tables
```{r Table S1, echo=FALSE, fig.cap="Variance inflation factors for the explanatory variables used in the analysis."}
knitr::include_graphics("tables/collinearity_investigation.pdf")
```

>>>>

# RESULTS
A total of 637,482 checklists provided a total of 5,944,819 observations of 580 different species which had > 100 observations. The least recorded species was Black-breasted Buttonquail (N=104) while the most recorded species was Australian Magpie (N=158,615). The mean ± SD number of observations for a species was 10,250 ± 19,269.19. Density plots of all 580 species' distributions of average radiance values are presented in Appendix 3.

@@

```{r Figure 1, echo=FALSE, fig.cap="An example of five different species' average radiance values."}
knitr::include_graphics("final figures & tables for ms/Figure1.pdf")
```

```{r Figure 2, echo=FALSE, fig.cap="The distribution, on a log-scale, of the response variable for the 477 species included in the analysis, with five example species highlighted."}
knitr::include_graphics("final figures & tables for ms/Figure2.pdf")
```

```{r Figure 3, echo=FALSE, fig.cap="A phylogenetic tree of the birds with the tips colored based on the urbanization index. The urbanization index is also shown based on the size of the bar associated with a species."}
knitr::include_graphics("final figures & tables for ms/Figure3.pdf")
```

```{r Figure 4, echo=FALSE, fig.cap="Parameter estimates for each of the four modelling approaches employed in the analysis. A star represents a significant effect. Note that the model-averaged results do not contain every possible predictor variable in the case that a given predictor variable was not included in the top model set."}
knitr::include_graphics("final figures & tables for ms/Figure4.pdf")
```

```{r Figure 5, echo=FALSE, fig.cap="Proportional differences for parameter estimates from the non-phylogenetically constrained and phylogenetically constrained models."}
knitr::include_graphics("final figures & tables for ms/Figure5.pdf")
```

# Tables
```{r Table 1, echo=FALSE, warning=FALSE, message=FALSE}
remake::dump_environment()

library(phylosignal)
   dplyr::select(analysis_data,body_size_logged,clutch_size_logged,response,range_size, #select appropriate rows
          nest_generalism,diet_generalism,breeding_habitat_generalism,feeding_habitat_generalism,brain_residual) ->dd

row.names(dd) <- analysis_data$binom #name rows so that it matches the tree
dd$rand <- rnorm(dim(dd)[2]) #random numbers to test package
p4d <- phylo4d(aus_bird_tree, dd) #create phylobase object

ps <- phyloSignal(p4d,reps = 9999)

Table1 <- ps$pvalue

row.names(Table1) <- c("log(Body size)", "log(Clutch size)", "Urbanization index", "Range size (1000s km2)",
                       "Nest generalism", "Diet generalism", "Breeding habitat generalism",
                       "Feeding habitat generalism", "Brain residual", "Rand")

library(kableExtra)

kable(Table1, format = "latex", caption = "Results showing the significance of the phylogenetic signal analyses.", booktabs = T) %>%
kable_styling(latex_options = c("striped", "hold_position"))

```

@@

```{r Figure S1, echo=FALSE, fig.cap="A correlation plot for the continuous variables used in the modelling procedures."}
knitr::include_graphics("final figures & tables for ms/FigureS1.pdf")
```

```{r Figure S2, echo=FALSE, fig.cap="Phylogenetic uncertainty for some of the most important predictor variables included in the analysis."}
knitr::include_graphics("final figures & tables for ms/FigureS2.pdf")
```

# Supplementary tables
```{r Table S1, echo=FALSE, warning=FALSE, message=FALSE}
library(kableExtra)

read_csv("Data/TableS1.csv")

kable(collinearity_investigation, format = "latex", caption = "Variance inflation factors for the explanatory variables used in the analysis.", booktabs = T) %>%
kable_styling(latex_options = c("striped", "hold_position"))

```

```{r Table S2, echo=FALSE, warning=FALSE, message=FALSE}
remake::dump_environment()

library(phylosignal)
   dplyr::select(analysis_data,body_size_logged,clutch_size_logged,response,range_size, #select appropriate rows
          nest_generalism,diet_generalism,breeding_habitat_generalism,feeding_habitat_generalism,brain_residual) ->dd

row.names(dd) <- analysis_data$binom #name rows so that it matches the tree
dd$rand <- rnorm(dim(dd)[2]) #random numbers to test package
p4d <- phylo4d(aus_bird_tree, dd) #create phylobase object

ps <- phyloSignal(p4d,reps = 9999)

TableS2 <- ps$stat

row.names(TableS2) <- c("log(Body size)", "log(Clutch size)", "Urbanization index", "Range size (1000s km2)",
                       "Nest generalism", "Diet generalism", "Breeding habitat generalism",
                       "Feeding habitat generalism", "Brain residual", "Rand")

kable(TableS2, format = "latex", caption = "Summary statistics of the phylogenetic signal analysis.", booktabs = T) %>%
kable_styling(latex_options = c("striped", "hold_position"))

```
